Results section

### 2022-10-27 submission/manuscript.Rmd
Updated manuscript

#### Discussion of experimental results - Exp 2.
- Directionality of change varied, with alternating over- and under-expression of various cytokines. As can be seen in [*Cytokine plot of signif results *] pups tended to group based on feeding-scheme, with both formula-fed groups being either suppressed og over-expressed together, compared with breastfed groups, irrespective of antibiotics treatment. 
- This observation is supported by a a multiple linear regression analysis, evaluating the effects of MAT (AB or CON) and type of feed (BF of FF) separately and interactively. The analysis found statistically significant effects of formula feeding for REG_MODEL_CYTOKINES$TERM == TYPEOFFEED, with the greatest effect estimate of ESTIMATE$IL-6 , P-val$IL-6.

@@

#### Detailed description of Exp 3.
- In round 3 we repeated the experimental setup with regards to MAT, adding either Vancomycin, Gentamicin or sterile water to the drinking water of pregnant "females" (use same word throughout(mothers)). We repeated the group-setup from PreExp  1 and  separated pups into breastfeeding or formula feeding, for a total of 6 groups (see overview table). 
- All pups survived the experiment and were included in the final analysis. 
- 2 hours after FITC administtion pups were euthanized by decapitation and blood collected in eppendorfs for analysis of serum FITC concentration. Intestinal samples were collected for gene expression assays, histological assessment, pro-inflammatory cytokine analysis and gut microbiome sequencing.

>>>>

#### Discussion of experimental results - Exp 2.
- Weight development similar to Chen. 
- Whether it was a result of growth restriction or shorter gestational age is difficult to determine. 
- Chen et al. did not report whether dams were from the same day. 
- Intestinal permeability response was different depending of type of antibiotics. 
- Vancomycin decreased intestinal permeability whereas gentamicin increased it.
  - This has been shown in Winstar rats before (Thulstrup 2015). 
- Cytokine expression was most affected in the VANCO group.

- In summary:

@@

#### Rationale:
Based on the results from Exp 2 it was difficult to ascertain which treatment was more likely to manifest in NEC like phenotype. 
- Gentamicin had increased intestinal permeability the most. However, the greatest effect of cytokine expression was found with the vancomycin treatment. 
- In addition to this divergence, the interaction effect found in Exp 1 suggested it was likely that combining MAT with formula feeding would yield different results. 
- Therefore, we decided to increase the breeding population to allow for an experiment that combined both types of antibiotics with either formula-feeding or breastfeeding, for a total of 6 experimental groups.

#### Aim:

#### Conclusion:

#### Detailed description of Exp 3.
- In Exp 3 we repeated the experimental setup with regards to MAT, adding either Vancomycin, Gentamicin or sterile water to the drinking water of pregnant femailes. We repeated the group-setup from PreExp  1 and  separated pups into breastfeeding or formula feeding, for a total of 6 groups (see overview table). 
- All pups survived the experiment and were included in the final analysis. 
- 2 hours after FITC administtion pups were euthanized by decapitation and blood collected in eppendorfs for analysis of serum FITC concentration. Intestinal samples were collected for gene expression assays, histological assessment, pro-inflammatory cytokine analysis and gut microbiome sequencing.
